---
title: "Final Project"
subtitle: "Data Science for Biologists, Spring 2021"
author: "Ashley Priore"
output: 
  html_document:
    theme: cerulean
    highlight: tango
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# DON'T CHANGE THE NEXT LINE, except to add NEW options if you have any.
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = TRUE, include = TRUE, fig.width=6, fig.height=4)

# Load all libraries you use HERE:
library(tidyverse)
```

<br><br>

## Introduction

The pizza barstool review dataset comprises customer reviews of many different pizzerias all throughout the USA. This dataset provides the name of the pizzeria, general aspects regarding location, and customer's reviews based on pricing and overall experience. I chose this dataset because it interested me as I worked in a pizzeria for 5 years! I would like to further explore how different pizzerias are ranked in different areas. The link to this source is [Pizza](%5Bhttps://github.com/rfordatascience/tidytuesday/blob/master/data/2019/2019-10-01/pizza_barstool.csv). (<https://github.com/rfordatascience/tidytuesday/blob/master/data/2019/2019-10-01/pizza_barstool.csv>)

```{r read-examine-data}
#reading in dataset
pizza_barstool <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_barstool.csv")

#briefly viewing dataset
glimpse(pizza_barstool)

```

<br><br>

## Question 1

#### How many pizzerias are within each price level?

### Methods

```{r question one}
pizza_barstool%>% #giving this dataset to ggplot
  ggplot()+ #about to make a plot
  aes(x=price_level)+ #specifying x axis
  geom_bar(color= "black", fill="lightsteelblue1")+ #specifying type of plot, bins, color, and fill
  labs(x= "Price Level")+ #appropriate labeling and price level: 0= no $ (least expensive), 1=$, 2=$$, 3=$$$ (most expensive)+
  theme_minimal() #specifying theme 

pizza_barstool%>%
  count(price_level)
```

### Answer

The number of pizzerias surveyed that are within each price level are as follows: price level 0 (least expensive)= 21, price level 1= 216, price level 2= 218, and price level 3 (most expensive)= 8. 

<br><br>

## Question 2

#### What is the relationship bewteen latitude and longitude of these pizzerias?

### Methods

```{r question two}
pizza_barstool%>% #giving this dataset to next function
  ggplot()+ #about to make a plot
  aes(x=latitude, y=longitude)+ #specifying x and y axis 
  geom_point()+ #specifying type of plot
  geom_smooth(method="lm", se= FALSE, color="plum1")+ #adding in smooth trendline and specifying color
  labs(x= "Latitude", y= "Longitude")+ #appropriate labeling 
  theme_bw() #indicating theme 

```

### Answer

There is a positive relationship between latitude and longitude of the given pizzerias.

<br><br>

## Question 3

#### Does a price level of 2 have a higher total critic score compared to a price level of 1?

### Methods

```{r question three}
pizza_barstool%>% #giving this dataset to next function
  rename(critic_total_score= review_stats_critic_total_score)%>% #renaming column for easier use
  filter(price_level %in% c("1","2"))%>% #keeping only price levels of 1 and 2 ******************
  ggplot()+ #about to make a plot
  aes(x=price_level, y=critic_total_score)+ #specifying x and y axis
  geom_col(fill= "mediumspringgreen")+ #specifying type of plot and fill
  labs(x= "Price Level", y= "Critic Total Score")+ #appropriate labeling 
  theme_light() #indicating theme
  
```

### Answer

Price level of 2 did have a higher critic total score than compared to price level 1.

<br><br>

## Question 4

#### REPLACE TEXT WITH YOUR QUESTION. Your question should literally be a level-4 header.

### Methods

```{r question four}

```

### Answer

Replace this text with your answer to your question.
